### 2022-05-26 main/chapter_2ljets.tex
begin serious b-tagging section

My core contribution of this thesis is to the recent \atlas\
search ``for new phenomena in events with two leptons, jets, and
missing transverse momentum''~\cite{atlas2022searches}.
For brevity, I will call this search $\twoljets$.

@@

Jets in $\twoljets$ use the anti-$k_t$ algorithm with the standard small radius
parameter of $R=0.4$~\cite{jet_anti_kt}.
Jets are formed from ``topological'' clusters of energy deposits in the
calorimeters~\cite{atlas_jet_topo_PERF_2014_07}.

This topological clustering algorithm is not the latest \atlas\ jet algorithm;
it has been supplanted in recent years by a `particle flow' method, which
uses tracking information to improve the reconstruction of charged
hadrons~\cite{atlas_jet_pflow_PERF_2015_09}.
We did not switch to these improved jets because the change would have required
further delays.

Baseline jets are defined require $\pt > 20~\eV[G]$, and signal jets require
$\pt > 30~\eV[G]$.
Again, details of quality criteria and angular selections
The $\twoljets$ electroweak analysis uses only signal jets unless those jets
are $b$-tagged.

\subsubsection{$b$-tagging}
\label{sec:btagging}
Tagging adds additional labels to jets, and is particularly useful for
encoding flavour information derived from data within the jet cluster.
In particular, $b$-tagging attempts to identify jets originating from $b$
quarks, which have distinct features due to the long lifetimes and decay
channels of $B$ hadrons.

>>>>

My core contribution in this thesis is to the recent \atlas\
search ``for new phenomena in events with two leptons, jets, and
missing transverse momentum''~\cite{atlas2022searches}.
For brevity, I will call this search $\twoljets$.

@@

Jets in $\twoljets$ use the anti-$k_t$ algorithm with the standard small-radius
parameter of $R=0.4$~\cite{jet_anti_kt}.
Jets are formed from `topological' clusters of energy deposits in the
calorimeters~\cite{atlas_jet_topo_PERF_2014_07}.

This topological clustering algorithm is no longer the \atlas-recommended jet
algorithm; it has been supplanted in recent years by a `particle flow' method,
which uses tracking information to improve the reconstruction of charged
hadrons~\cite{atlas_jet_pflow_PERF_2015_09}.
We did not attempt to switch to these improved jets because the change in
policy occurred during the years this analysis was in development, and the
change would have required more work and even more delays.

Baseline jets are defined to require $\pt > 20~\eV[G]$ with $|\eta| < 2.8$;
signal jets additionally require $\pt > 30~\eV[G]$.
To reduce the impact of pile-up jets, a variety of quality criteria are used,
depending on the jet $\pt$ and $|\eta|$.
Details of these quality criteria and angular selections are given in the
paper~\cite{atlas2022searches}.

\subsubsection{$b$-tagging}
\label{sec:btagging}

Tagging adds labels to objects.
For jets in $\twoljets$, $b$-tagging is used to identify jets which are
more likely to have originated from $b$ quarks;
these tags serve to improve our separation of $t\bar t$ backgrounds and
of signals producing $Z/h \rightarrow b\bar b$ decays.

Signal $b$-tagged jets require $\pt > 20~\eV[G]$, $|\eta| < 2.5$ and a tag from
the `MV2c10' algorithm at its $77\%$ efficiency working point.
\TODO{cite, summarize}

encode information derived from data within the jet cluster.
In particular, $b$-tagging attempts to identify jets originating from $b$
quarks, which have distinct features due to the long lifetimes and decay
channels of $B$ hadrons.
